% Possible options include font size ('10pt', '11pt' and '12pt'),
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper',
% 'executivepaper' and 'landscape') and font family ('sans' and 'roman').
\documentclass[11pt,a4paper,sans]{moderncv}

% Modern themes.
% Style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'.
\moderncvstyle{banking}

% Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and
% 'black'.
\moderncvcolor{blue}

% To set the default font; use '\sfdefault' for the default sans serif font,
% '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}

% Uncomment to suppress automatic page numbering for CVs longer than one page.
%\nopagenumbers{}

% Character encoding.
\usepackage[utf8]{inputenc}

% Adjust the page margins.
\usepackage[scale=0.75]{geometry}

% If you want to change the width of the column with the dates.
%\setlength{\hintscolumnwidth}{3cm}

\usepackage{import}

% Used in the command for typesetting "C++".
\usepackage{relsize}
\usepackage{xspace}

% Personal data.
\name{Ben}{Smith}
\address{1260 Republican St, Apt. 620, Seattle, WA 98109}{}{}
\phone[mobile]{214 803 3918}
\email{smithbr95@gmail.com}

%\homepage{www.myname.webs.com}

% Bibliography portions are commented out as they are not necessary for my
% purposes.

% To show numerical labels in the bibliography (default is to show no labels);
% only useful if you make citations in your resume.
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% Consider replacing the above by this.
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

% Bibliography with mutiple entries.
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%-------------------------------------------------------------------------------
%                                 Content
%-------------------------------------------------------------------------------
\begin{document}

\makecvtitle

% Introductory statement.
\small{Experienced software engineer interested in ...}

\section{Experience}

\vspace{6pt}

\begin{itemize}

\item{\cventry{July 2013--August 2013}{Construction Site Operative}{Eurogold Groundworks and Civil Engineering}{Moston}{}{\vspace{3pt}I was responsible for the administrative duties and the tidiness and general order of the site. I worked in a safety-oriented manner, often working alongside construction plant and machinery. At the end of my work with the company my colleagues praised my work ethic.}}

\vspace{6pt}

\item{\cventry{2009--2011}{Waiter, Catering and Banqueting}{Lavender Best Western Park Hall Hotel}{Charnock Richard}{}{\vspace{3pt}I worked for three years as a team leader providing silver service at weddings, stag/hen nights, and business conferences. I was often trusted with other jobs such as setting up conference rooms, moving beds around the hotel, and guiding big groups of customers to their rooms. As a team leader I would delegate tasks to a team of about 5 people, often new staff who needed training, and lead the group to service. During this time I worked in a highly professional manner and was focused to provide excellent customer service, even during high stress functions and events.}}

\vspace{6pt}

\item{\cventry{January 2008}{Assistant Electrician}{Ryan Electricals}{Southport}{}{\vspace{3pt}I spent a week working as an assistant electrician as part of my high school work experience. My roles included wiring plugs, tidying, and assisting with household electrical repairs and fittings.}}

\end{itemize}

\section{Education}

\vspace{5pt}

\begin{itemize}

  \item{\cventry{2014--2018}{Bachelor of Science in Computer Science}
    {Texas A\&M University}{College Station, TX}{Minor in Mathematics}
    {University Research Scholar \\ Overall GPA: 3.38 \\ Major GPA: 3.62}}

\end{itemize}

\section{Technical and Personal skills}

\vspace{6pt}

\begin{itemize}

\newcommand{\Rplus}{\protect\hspace{-.1em}\protect\raisebox{.35ex}{\smaller{\smaller\textbf{+}}}}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}\xspace}

\item \textbf{Programming Languages:} \\
  Experienced: \Cpp, C, Python \\
  Basic understanding: Java, Haskell, JavaScript.

\vspace{6pt}

\item \textbf{Industry Software Skills:} SolidWorks (Advanced), Matlab (Advanced), Ansys (Intermediate),  LTspice (Intermediate), Most MS Office products including MS project and MS access (Advanced).

\end{itemize}


% Reference section is commented out because I don't need it for my purposes.

%\section{References}
%
%\vspace{6pt}
%
%\begin{itemize}
%
%\item{Up to 4 references available on request}
%
%\end{itemize}

% Publications from a BibTeX file without multibib for numerical labels.
% Consider merging with preamble part.
%\renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}

% To redefine the heading string ("Publications"):
%\renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}

% Publications from a BibTeX file using the multibib package.
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}

\end{document}
